KeysarMouseTracking.csv

### 2016-01-21 experiment1/analysis/exp1Analysis.Rmd
Updated analysis scripts

```{r}
setwd('~/Repos/psych254/replication_project/analysis/')
mouseD = read.csv('fullSampleMouse.csv')
errorD = read.csv('fullSampleError.csv')
messageD = read.csv('fullSampleMessage.csv')
str(mouseD)
library(tidyr)
library(dplyr)
library(ggplot2)
```

@@

```{r}
nonCriticalMistakes <- errorD %>%
  # only look at mistakes on noncritical (filler) items
  filter(critical != 1) %>%
  # don't want to double-count people for messing the same thing up multiple times
  filter(attemptNum == 0) %>% 
  group_by(gameid) %>%
  tally() %>%
  # implement exclusion criteria of errors on >~10% of non-critical trials
  filter(n >= 2)

@@

```{r}
eD <- errorD %>%
  filter(!(gameid %in% bannedIDs)) %>%
  filter(critical == 1) %>%
  filter(attemptNum == 0) %>%
  group_by(gameid, condition) %>%
  tally() %>%
  mutate(cond2 = as.numeric(n >= 2)) %>%
  group_by(condition) %>%
  summarise(atLeastOnce = length(n)/14, 
            atLeastTwice = sum(cond2)/14)
eD

@@

g <- (ggplot(heatMapForPlot, aes(x = condition, y = percent, group = cellType,
                                  color = cellType)) 
      + geom_line(aes(linetype = cellType), size = 2)
      + geom_errorbar(aes(ymax = percent + error, 
                          ymin = percent - error), size =2 ,
                      width = 0.1))
g
```

>>>>

```{r}
setwd('~/Repos/keysar_replication/experiment1/analysis/')
mouseD = read.csv('fullSampleMouse.csv')
errorD = read.csv('fullSampleError.csv')
messageD = read.csv('fullSampleMessage.csv')
str(mouseD)
library(tidyr)
library(dplyr)
library(ggplot2)
```

@@

```{r}
numParticipants <- length(unique(mouseD$gameid))
nonCriticalMistakes <- errorD %>%
  # only look at mistakes on noncritical (filler) items
  filter(critical != 1) %>%
  # don't want to double-count people for messing the same thing up multiple times
  filter(attemptNum == 0) %>% 
  group_by(gameid) %>%
  tally() %>%
  # implement exclusion criteria of errors on >~10% of non-critical trials
  filter(n >= 2)

@@

```{r}
eD <- errorD %>%
  filter(!(gameid %in% bannedIDs)) %>%
  filter(critical == 1) %>%
  filter(attemptNum == 0) %>%
  group_by(gameid, condition) %>%
  tally() %>%
  mutate(cond2 = as.numeric(n >= 2)) %>%
  group_by(condition) %>%
  summarise(atLeastOnce = length(n)/14, 
            atLeastTwice = sum(cond2)/14,
            total = sum(n) / (4 * numParticipants))
eD

@@

g <- (ggplot(heatMapForPlot, aes(x = condition, y = percent, group = cellType,
                                  color = cellType)) 
      + geom_line(aes(linetype = cellType), size = 2)
      + geom_errorbar(aes(ymax = percent + error, 
                          ymin = percent - error), size =2 ,
                      width = 0.1)
      + ggtitle("Experiment 1 Hover-Time"))
ggsave("../../writing/cogsci-submission/images/exp1MouseTracking.pdf")
```
